%% start of file `template.tex'.

\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
\usepackage{fontspec}
\defaultfontfeatures{
    Path = /usr/local/texlive/2018/texmf-dist/fonts/opentype/public/fontawesome/  }
\usepackage{fontawesome}
% modern themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.80]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

\usepackage{import}

% personal data
\name{Sagnika}{Dasgupta}
%\title{CV}                               % optional, remove / comment the line if not wanted
\address{1263, 2nd Cross, 2nd Main, HAL 3rd Stage, New Tippasandra, Bangalore 560075}{}{}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+91 9538766397}                   % optional, remove / comment the line if not wanted
%\phone[fixed]{01234 123456}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{sagnika.dasgupta29@gmail.com}                               % optional, remove / comment the line if not wanted
%\homepage{www.myname.webs.com}                         % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{MaryamCvPic}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage{wrapfig}


\begin{document}
\makecvtitle

\small{Currently working on curation, analysis and mining of research data. Previous experience in event and project management in environment related issues. Work well in teams and projects with multiple stakeholders.}

\section{Professional Experience}
    \vspace{5pt}

\begin{itemize}


    \item{\cventry{Jul 2018 - Present}{Molecular Connections}{Scientific Analyst}{Bangalore, KA}{}{}{}}
    \vspace{2mm}
    \textbf{Key Responsibilities}
    \begin{itemize}
        \item Scientific Curation and Formulation of Abstracts for Patents and Research articles   Japanese, Korean, Chinese and English languages, in the fields of \\
            \textit{ \textbullet{} Immunology \textbullet{}  Biochemistry,\textbullet{}  Pathology \textbullet{}  Pharmacology\textbullet{}  Toxicology\textbullet{}  Oncology\textbullet{}   Environmental Science\textbullet{} Electrochemical Technology\textbullet{}  Semiconductor Physics \textbullet{} Nanotechnology}
    \item Analyzing the roles of the drug, protein, genes and estimating adverse drug reaction in a disease condition.
        \begin{itemize}
            \item Semantic clinical data indexing, curation and abstraction of  articles and patents.
            \item Identifying interacting proteins and other targets through protein interaction.
        \end{itemize}
    \end{itemize}

        
    \vspace{4mm}


    \item{\cventry{Jan 2016– Aug 2016}{Daily Dump}{Event Coordinator}{Bangalore, KA}{}{}{}}
    \vspace{2mm}

    \textbf{Key Responsibilities}
    \begin{itemize}
        \item Schedule sensitization
        \item Awareness programme and training for clients
        \item Handling customer related issues
        \item Maintaining the CRM by entering the leads generated daily
        \item Reporting and documentation of awareness programme
    \end{itemize}

    \vspace{4mm}
    \item{\cventry{Sep 2013 – Dec 2015}{Centre for Environment Education}{Project Associate}{Kolkata, WB}{}{ }{}}
    \vspace{2mm}

    \textbf{Key Responsibilities}

    \begin{itemize}
            \item Networking with experts and professors for guidance and involvement of new techniques for use of fly
                  ash in agriculture field land reclamation and agriculture in experimental basis and overall management
                  of fly ash (\textbf{Nabadiganta Project on Fly Ash Management and Community Development})
            \item Increasing evironment awareness by enabling Eco clubs in 30+ schools(\textbf{Urja Chetna Project})
            \item Documentation and reporting
            \begin{itemize}
                \item Bengali Trans-adaptation of Science Express Climate Actions Special (SECAS) documents
                \item Proposal for improving Municipal Solid Waste Management
            \end{itemize}
            \item Event management
            \begin{itemize}
                \item Urban Climate Change Resilience Project with NIUA
                \item Sankalp Diwas 2014, an initiation of CEE in collaboration with National Clean Ganga Mission (NCGM) at Farakka, West Bengal.
                \item Paryavaran Mitra Puraskar Award event 2013-14
             \end{itemize}
    \end{itemize}

\end{itemize}

\pagebreak

\section{Education}


    \vspace{5pt}

    \begin{itemize}

    \item{\cventry{2016 - 2018}{Garden City College}{M.Sc. BioTechnology}{Bangalore, WB}{}{ }{\textbf{Project}: Green Synthesis and characterization of Selenium Nanoparticles and its Therapeutic Effects}}
    \vspace{4mm}

    \item{\cventry{2011 - 2013}{University of Kalyani}{M.Sc. Environmental Management}{Kalyani, WB}{}{ }{\textbf{Project}: Cultivation of Chlorella in live stock waste water for nutrient reclamation}}
    \vspace{4mm}

    \item{\cventry{2007 - 2011}{Vivekananda College for Women}{B.Sc. Zoology}{Kolkata, WB}{}{}{}}
    \vspace{4mm}

    \item{\cventry{2005 - 2007}{Sir Ramesh Mitter Girls High School}{WBCHSE(10+2)}{Kolkata, WB}{}{}{}}
    \vspace{4mm}

    \item{\cventry{2005}{Sri Sarada Ashram Balika Vidyalaya}{WBBSE(10)}{Kolkata, WB}{}{}{}}
    \vspace{4mm}


\end{itemize}

\section{Others Skills}
\begin{itemize}
        \item \textbf{Vermicomposting}
        \item \textbf{Computer Proficiency}: MS-Office. Basics of Nebcutter, Primer9, ClustalOmega
        \item \textbf{Business Skills}: Good presentation skills, Team player. Experienced Event manager
        \item \textbf{Linguistic Profeciency}: English, Bengali, Hindi
\end{itemize}

\end{document}




